Tunnels to Towers: Secure Virtual Private Networking for CCN

### 2017-04-06 paper/05-sec-analysis.tex
paper

\textbf{Adversary Goals and Capabilities.} The goal of the adversary is either 1) to retrieve any information associated with the original issued interest $I_p$ and/or the original content $C_p$ or 2) to retrieve the identities of the consumer and/or producer, thus violating the anonymity in the communication. An adversary is also considered successful if it is able to impersonate the content producer by faking a content response. Since the original interest and the original content are visible inside the consumer and producer domains, we here assume that the adversary cannot eavesdrop or compromise hosts inside such domains. It is also worth to emphasize that, by the conceptual design of the VPN, communication is anonymous to hosts from outside the VPN but not to hosts that belong to that VPN. Anyhow, one-to-one anonymous communication is still achievable sing the VPN paradigm if the communication must be anonymous to any other host in the network\footnote{In the case that communication should be anonymous even to nodes inside the consumer and producer domains, $G_c$ and $G_p$ could be ran as processes within the consumer and producer hosts, respectively. This way, packets exchanged between them would remain anonymous to any other node in the network}. This also means that, as components of the producer and consumer domains, we assume that the gateways $G_c$ and $G_p$ cannot be compromised.

>>>>

\textbf{Adversary Goals and Capabilities.} The goal of the adversary is either 1) to retrieve any information associated with the original issued interest $I_p$ and/or the original content $C_p$ or 2) to retrieve the identities of the consumer and/or producer, thus violating the anonymity in the communication. An adversary is also considered successful if it is able to impersonate the content producer by faking a content response. Since the original interest and the original content are visible inside the consumer and producer domains, we here assume that the adversary cannot eavesdrop or compromise hosts inside such domains. It is also worth to emphasize that, by the conceptual design of the VPN, communication is anonymous to hosts from outside the VPN but not to hosts that belong to that VPN. Anyhow, one-to-one anonymous communication is still achievable sing the VPN paradigm if the communication must be anonymous to any other host in the network. This also means that, as components of the producer and consumer domains, we assume that the gateways $G_c$ and $G_p$ cannot be compromised.

### 2017-04-06 paper/07-experiment.tex
paper

CCVPN is implemented as a networking layer service running on the gateways of private networks (see Fig.\ref{fig:ccvpn}).
Our implementation uses the CCNx software stack~\cite{CCNxGithub} and the cryptographic library Sodium~\cite{sodiumGithub}. These are both publicly available and are written in C.
The interest encapsulation routine (Alg.\ref{alg:interestEncap}) is implemented using

In this section we empirically evaluate the CCVPN design paying special attention to the metrics that were earlier discussed in Sec.~\ref{sec:analysis}, i.e., processing overhead, network throughput, and state consumption. In our evaluation we consider the two versions of CCVPN: public key version, and symmetric key version. We here recall that the symmetric key version relies on the assumption that a secure key agreement protocol is performed between the domain's gateways prior to the CCVPN protocol execution.

Our testbed network consists of a butterfly topology, in which the consumers' side and the producers' side gateways are directly interconnected. $N$ producers are connected to the producers' domain gateway and $M$ consumers are connected to the consumers' domain gateway (see Fig.~\ref{create_figure}).

@@

\begin{table}[!h]
\centering
\caption{Interest encapsulation processing times}
\label{my-label}
\begin{tabular}{|l|l|l|l|l|}
\hline
Encapsulation mode   & Encapsulation & Decapsulation \\ \hline
Public Key  & 444$\mu s$           & 449$\mu s$           \\ \hline \cline{4-5} 
Symmetric Key & TODO          & TODO          \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{figure}[]
\centering
\includegraphics[width=\columnwidth]{images/testnet.eps}
\caption{Testbed network topology. $M$ consumers and $N$ producers}\label{testnet}
\end{figure}

CCVPN is implemented as a network layer service running on the gateways of the private networks that compose the VPN (see Fig.\ref{fig:ccvpn}).
Our implementation uses the CCNx software stack~\cite{CCNxGithub} and the cryptographic library Sodium~\cite{sodiumGithub}. These are both publicly available and written in C.
For the PKE version of CCVPN, we use Sodium Sealed-Boxes~\cite{bernstein2006curve25519}, implemented over X25519 elliptic curves, as the PKE algorithm for the interest encapsulation and decapsulation routines (Algorithm~\ref{alg:interestEncap}, and Algorithm~\ref{alg:interestDecap} of Sec.~\ref{metho}).
AES256-GCM~\cite{dworkin2007recommendation} is used to encrypt-then-MAC content responses (Alg.~\ref{alg:contentEnc}, and Alg.~\ref{alg:contentDec} of Sec.~\ref{metho}).
Recall that the symmetric keys used to encrypt-then-MAC the content packets are generated and sent together with the encapsulated interest in Alg.~\ref{alg:interestEncap}.
In the symmetric key version of the design, both, interests and contents, are encapsulated using AES256-GCM under the assumption that the gateways already share symmetric key.

The experiments presented throughout this section were executed in an Intel Core i7-3770 octacore CPU @3.40GHz, with 16GB of RAM, running Linux (Ubuntu 14.04LTS). Content payload sizes were set to 10 kilobytes.
On every experiment, each of the two gateway processes (i.e., consumer side gateway process, and producer side gateway process) were assigned as a high priority processes and each of them ran in a single core of the processor.
Table~\ref{should_be_figure} (\todo{Should be a single figure w/ six boxplots}) presents boxplots for the execution times of the four algorithms involved in CCVPN's data transmission, including both, PKE and Symm. Key versions for interest encapsulation and decapsulation.

\begin{table}[!h]
\centering
\caption{Interest encapsulation processing times}
\label{should_be_figure}
\begin{tabular}{|l|l|l|l|l|}
\hline
Encapsulation mode   & Encapsulation & Decapsulation \\ \hline
Public Key  & 444$\mu s$           & 449$\mu s$           \\ \hline \cline{4-5} 
Symmetric Key & TODO          & TODO          \\ \hline
\end{tabular}
\end{table}

With the goal of evaluating the impact of CCVPN's cryptographic overhead on the overall network performance, we measure the network throughput and the request-response round trip time (RTT) under different topology settings.
In our testbed network, the consumers' side and the producers' side gateways are directly interconnected. $N$ producers are connected to the producers' domain gateway and $M$ consumers are connected to the consumers' domain gateway, as illustrated in Fig.~\ref{testnet}.
Under such topology we consider three variations for the values of ${M,N}$:

\begin{itemize}
 \item \textbf{One consumer and one producer $[1,1]$}:
 \item \textbf{Multiple consumers and one producer $[M,1]$}:
 \item \textbf{Multiple consumers and multiple producers $[M,N]$}:
\end{itemize}

@@
